Male-biased sexual selection, but not sexual dichromatism, predicts speciation in birds

### 2020-08-23 Sexual Selection and Speciation.Rmd
slight changes to manuscript and figure

**Table S7:** The estimates of the MCC models plotted above are based on the following data tables.
```{r Values For Models}
MCC.DR.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC DR Estimates", split.table = Inf)
MCC.ND.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC ND Estimates", split.table = Inf)
MCC.lambda.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Speciation Estimates", split.table = Inf)
MCC.mu.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Extinction Estimates", split.table = Inf)
```

@@

**Table S8:**  HPD intervals calculated for the above figure (*i.e.* models using RGB values of sexual dichromatism). The HPD range is determined using the ``hdi`` function with a 95 % credible interval. These intervals do not take into account the variance associated with each interval and thus are not an estimate of model precision. Intervals not overlapping zero suggest that 95 % of trees from the posterior generate a model estimate for the given parameter that is in the same direction (+ or -).
```{r HPD, warning = FALSE}
hpd.DR.top <- list()
for(x in unique(DR.pgls.summary$Parameter)) {
hpd.DR.top[[x]] = hdi(DR.pgls.summary %>% filter(Parameter == x) %>% dplyr::select("Estimate"))
}
hpd.DR.top <- bind_rows(hpd.DR.top) %>% `rownames<-`(c("Lower", "Upper")) %>% dplyr::select(-"(Intercept)")

@@

**Table S9:** Model estimates from $\lambda_{BAMM}$ and $\mu_{BAMM}$ tip-rate estimates show high levels of variability between trees relative to estimates from $\lambda_{DR}$ and $\lambda_{ND}$. The interval ratio is calculated as the width of the HPD 95 % CI relative to the MCC 95 % CI. A value of 1 suggests that model estimates from 95 % of the trees fall within the MCC 95 % CI. Here, the large values for the estimates from BAMM tip-rates suggest that there is high variation in tip-rate estimates across trees that is not see within the DR and ND models.
```{r HPD CI interval ratio}
hpd.DR.top2 <- hpd.DR.top %>% t() %>% as.data.frame() %>% rownames_to_column(var = "Parameter")
hpd.DR.top2$HPD.Interval <- hpd.DR.top2$Upper - hpd.DR.top2$Lower
DR.intervals <- left_join(hpd.DR.top2, MCC.DR.summary, by = "Parameter")
DR.intervals$MCC.Interval <- DR.intervals$UCI - DR.intervals$LCI
DR.intervals$DR.IntervalRatio <- hpd.DR.top2$HPD.Interval/DR.intervals$MCC.Interval

@@

**Table S10:** The dredged models using a subset of species for which sexual dichromatism was measured using spectrophotometry. All four show the top model is one with no interactions, with $\delta AICc > 4$.
```{r Armenta dredged}
Armenta.dredged.ND.model <- readRDS("data/Armenta.dredged.ND.model.rds")
Armenta.dredged.DR.model <- readRDS("data/Armenta.dredged.DR.model.rds")
Armenta.dredged.spec.model <- readRDS("data/Armenta.dredged.spec.model.rds")
Armenta.dredged.extinct.model <- readRDS("data/Armenta.dredged.extinct.model.rds")

@@

**Table S11:** MCC estimates from the above plot are presented as numerical values below. 
```{r Armenta moel summary}
Armenta.MCC.DR.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC DR Estimates from Spec measures")
Armenta.MCC.ND.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC ND Estimates from Spec measures")
Armenta.MCC.Lambda.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Speciation Estimates from Spec measures")
Armenta.MCC.Mu.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Extinction Estimates from Spec measures")
```

**Table S12:**  HPD intervals calculated for the above figure (*i.e.* models using Spectrophotometry values of sexual dichromatism). These intervals do not take into account the variance associated with each estimate and thus are not an estimate of model precision. Intervals not overlapping zero suggest that 95 % of trees from the posterior generate a model estimate for the given parameter that are in the same direction (+ or -). These intervals are calculated in the same way as in Table S7.
```{r Armenta HPD, warning = FALSE}
Armenta.hpd.DR.top <- list()
Armenta.DR.pgls.summary <- na.omit(Armenta.DR.pgls.summary)
for(x in unique(Armenta.DR.pgls.summary$Parameter)) {
Armenta.hpd.DR.top[[x]] = hdi(Armenta.DR.pgls.summary %>% filter(Parameter == x) %>% dplyr::select(Estimate))
}
Armenta.hpd.DR.top <- bind_rows(Armenta.hpd.DR.top) %>% `rownames<-`(c("Lower", "Upper"))

@@

**Table S13:** All top models ($\delta AICc > 4$) using male-biased sexual selection measures do not contain interactions between sexual selection and the environmental variables. Thus interaction terms were not included in further analysis.

@@

**Table S14:** MCC model estimates from the above model are presented here as numberical values with 95 % CIs.
```{r Table for SS plots}
Subset.MCC.DR.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC DR Estimates from Male-bias SS", split.table = Inf)
Subset.MCC.ND.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC ND Estimates from Male-bias SS", split.table = Inf)
Subset.MCC.Lambda.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Speciation Estimates from Male-bias SS", split.table = Inf)
Subset.MCC.Mu.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Extinction Estimates from Male-bias SS", split.table = Inf)
```

**Table S15:** HPD intervals are calculated for the above figure (i.e. models using Male-bias sexual selection measures). using this measure the models using $\lambda_{DR}$ have model estimates that fall on the positive side 95 % of the time in 100 trees. For $\lambda_{ND}$, there is a positive skew, however the 95 % HPD interval overlaps zero. $\lambda_{BAMM}$ also shows a lesser positive skew. These intervals do not take into account the variance associated with each estimate and thus are not an estimate of model precision. Intervals not overlapping zero suggest that 95 % of trees from the posterior generate a model estimate for the given parameter are in the same direction (+ or -). These intervals are calculated in the same way as in Table S7 and Table S9.  
```{r SS HPD, warning = FALSE}
Subset.hpd.DR.top <- list()
Subset.DR.pgls.summary <- na.omit(Subset.DR.pgls.summary)
for(x in unique(Subset.DR.pgls.summary$Parameter)) {
Subset.hpd.DR.top[[x]] = hdi(Subset.DR.pgls.summary %>% filter(Parameter == x) %>% dplyr::select(Estimate))
}
Subset.hpd.DR.top <- bind_rows(Subset.hpd.DR.top) %>% `rownames<-`(c("Lower", "Upper"))

@@

Subset.ND.plot <-Subset.ND.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6), fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1, colour="black", fill="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-0.25, 0.25)) +
  annotate("text", x=-0.22, y=1.5, label= expression(lambda[ND])) + xlab(" ") + ylab(" ") +
  geom_errorbarh(data = HPD_Interval_ND_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  theme(panel.grid.major.y = element_blank())
  # geom_text(aes(y=Parameter, x = Estimate, label=""), position = position_nudge(y = -0.8), inherit.aes = F)

@@

Subset.DR.plot <-Subset.DR.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1,fill="black", colour="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-0.25, 0.25))+
  annotate("text", x=-0.22, y=1.5, label= expression(lambda[DR])) + xlab(" ") + ylab(" ") + 
    geom_errorbarh(data = HPD_Interval_DR_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  theme(panel.grid.major.y = element_blank())

@@

Subset.B.plot <-Subset.B.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1,fill="black", colour="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-0.25, 0.25)) +
  annotate("text", x=-0.20, y=1.5, label= expression(lambda[BAMM])) +
  geom_errorbarh(data = HPD_Interval_B_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  xlab("Estimate (paternal care)") + ylab("") +
  theme(panel.grid.major.y = element_blank())

@@

Subset.ND.plot2 <-Subset.ND.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6), fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1, colour="black", fill="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-2.5, 4)) +
  xlab(" ") + ylab(" ") +
    geom_errorbarh(data = HPD_Interval_ND_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

@@

Subset.DR.plot2 <-Subset.DR.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1,fill="black", colour="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-2.5, 4)) +
  xlab(" ") + ylab(" ") +
  geom_errorbarh(data = HPD_Interval_DR_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

@@

Subset.B.plot2 <-Subset.B.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0.5, size = 1,fill="black", colour="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-2.5, 4)) +
  xlab("Estimate (sexual size dimorphism)") + ylab("") +
  geom_errorbarh(data = HPD_Interval_B_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.DR.pgls.summary <- dr.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|Intercept")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% Polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% Polygny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% Polygny", 
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.DR.pgls.summary$Parameter <- factor(Subset.DR.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% Polygyny", "5-20% Polygny", ">20% Polygny"))

@@

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.ND.pgls.summary <- nd.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|Intercept")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% Polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% Polygny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% Polygny",
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.ND.pgls.summary$Parameter <- factor(Subset.ND.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% Polygyny", "5-20% Polygny", ">20% Polygny"))

@@

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.B.pgls.summary <- b.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|(Intercept)")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% Polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% Polygny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% Polygny", 
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.B.pgls.summary$Parameter <- factor(Subset.B.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% Polygyny", "5-20% Polygny", ">20% Polygny"))

>>>>

**Table S8:** The estimates of the MCC models plotted above are based on the following data tables.
```{r Values For Models}
MCC.DR.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC DR Estimates", split.table = Inf)
MCC.ND.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC ND Estimates", split.table = Inf)
MCC.lambda.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Speciation Estimates", split.table = Inf)
MCC.mu.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Extinction Estimates", split.table = Inf)
```

@@

**Table S9:**  HPD intervals calculated for the above figure (*i.e.* models using RGB values of sexual dichromatism). The HPD range is determined using the ``hdi`` function with a 95 % credible interval. These intervals do not take into account the variance associated with each interval and thus are not an estimate of model precision. Intervals not overlapping zero suggest that 95 % of trees from the posterior generate a model estimate for the given parameter that is in the same direction (+ or -).
```{r HPD, warning = FALSE}
hpd.DR.top <- list()
for(x in unique(DR.pgls.summary$Parameter)) {
hpd.DR.top[[x]] = hdi(DR.pgls.summary %>% filter(Parameter == x) %>% dplyr::select("Estimate"))
}
hpd.DR.top <- bind_rows(hpd.DR.top) %>% `rownames<-`(c("Lower", "Upper")) %>% dplyr::select(-"(Intercept)")

@@

**Table S10:** Model estimates from $\lambda_{BAMM}$ and $\mu_{BAMM}$ tip-rate estimates show high levels of variability between trees relative to estimates from $\lambda_{DR}$ and $\lambda_{ND}$. The interval ratio is calculated as the width of the HPD 95 % CI relative to the MCC 95 % CI. A value of 1 suggests that model estimates from 95 % of the trees fall within the MCC 95 % CI. Here, the large values for the estimates from BAMM tip-rates suggest that there is high variation in tip-rate estimates across trees that is not see within the DR and ND models.
```{r HPD CI interval ratio}
hpd.DR.top2 <- hpd.DR.top %>% t() %>% as.data.frame() %>% rownames_to_column(var = "Parameter")
hpd.DR.top2$HPD.Interval <- hpd.DR.top2$Upper - hpd.DR.top2$Lower
DR.intervals <- left_join(hpd.DR.top2, MCC.DR.summary, by = "Parameter")
DR.intervals$MCC.Interval <- DR.intervals$UCI - DR.intervals$LCI
DR.intervals$DR.IntervalRatio <- hpd.DR.top2$HPD.Interval/DR.intervals$MCC.Interval

@@

**Table S11:** The dredged models using a subset of species for which sexual dichromatism was measured using spectrophotometry. All four show the top model is one with no interactions, with $\delta AICc > 4$.
```{r Armenta dredged}
Armenta.dredged.ND.model <- readRDS("data/Armenta.dredged.ND.model.rds")
Armenta.dredged.DR.model <- readRDS("data/Armenta.dredged.DR.model.rds")
Armenta.dredged.spec.model <- readRDS("data/Armenta.dredged.spec.model.rds")
Armenta.dredged.extinct.model <- readRDS("data/Armenta.dredged.extinct.model.rds")

@@

**Table S12:** MCC estimates from the above plot are presented as numerical values below. 
```{r Armenta moel summary}
Armenta.MCC.DR.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC DR Estimates from Spec measures")
Armenta.MCC.ND.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC ND Estimates from Spec measures")
Armenta.MCC.Lambda.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Speciation Estimates from Spec measures")
Armenta.MCC.Mu.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Extinction Estimates from Spec measures")
```

**Table S13:**  HPD intervals calculated for the above figure (*i.e.* models using Spectrophotometry values of sexual dichromatism). These intervals do not take into account the variance associated with each estimate and thus are not an estimate of model precision. Intervals not overlapping zero suggest that 95 % of trees from the posterior generate a model estimate for the given parameter that are in the same direction (+ or -). These intervals are calculated in the same way as in Table S9.
```{r Armenta HPD, warning = FALSE}
Armenta.hpd.DR.top <- list()
Armenta.DR.pgls.summary <- na.omit(Armenta.DR.pgls.summary)
for(x in unique(Armenta.DR.pgls.summary$Parameter)) {
Armenta.hpd.DR.top[[x]] = hdi(Armenta.DR.pgls.summary %>% filter(Parameter == x) %>% dplyr::select(Estimate))
}
Armenta.hpd.DR.top <- bind_rows(Armenta.hpd.DR.top) %>% `rownames<-`(c("Lower", "Upper"))

@@

**Table S14:** All top models ($\delta AICc > 4$) using male-biased sexual selection measures do not contain interactions between sexual selection and the environmental variables. Thus interaction terms were not included in further analysis.

@@

**Table S15:** MCC model estimates from the above model are presented here as numberical values with 95 % CIs.
```{r Table for SS plots}
Subset.MCC.DR.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC DR Estimates from Male-bias SS", split.table = Inf)
Subset.MCC.ND.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC ND Estimates from Male-bias SS", split.table = Inf)
Subset.MCC.Lambda.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Speciation Estimates from Male-bias SS", split.table = Inf)
Subset.MCC.Mu.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Extinction Estimates from Male-bias SS", split.table = Inf)
```

**Table S16:** HPD intervals are calculated for the above figure (i.e. models using Male-bias sexual selection measures). using this measure the models using $\lambda_{DR}$ have model estimates that fall on the positive side 95 % of the time in 100 trees. For $\lambda_{ND}$, there is a positive skew, however the 95 % HPD interval overlaps zero. $\lambda_{BAMM}$ also shows a lesser positive skew. These intervals do not take into account the variance associated with each estimate and thus are not an estimate of model precision. Intervals not overlapping zero suggest that 95 % of trees from the posterior generate a model estimate for the given parameter are in the same direction (+ or -). These intervals are calculated in the same way as in Table S9.  
```{r SS HPD, warning = FALSE}
Subset.hpd.DR.top <- list()
Subset.DR.pgls.summary <- na.omit(Subset.DR.pgls.summary)
for(x in unique(Subset.DR.pgls.summary$Parameter)) {
Subset.hpd.DR.top[[x]] = hdi(Subset.DR.pgls.summary %>% filter(Parameter == x) %>% dplyr::select(Estimate))
}
Subset.hpd.DR.top <- bind_rows(Subset.hpd.DR.top) %>% `rownames<-`(c("Lower", "Upper"))

@@

Subset.ND.plot <-Subset.ND.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6), fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0, size = 1, colour="black", fill="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-0.25, 0.25)) +
  annotate("text", x=-0.22, y=1.5, label= expression(lambda[ND])) + xlab(" ") + ylab(" ") +
  geom_errorbarh(data = HPD_Interval_ND_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  theme(panel.grid.major.y = element_blank())
  # geom_text(aes(y=Parameter, x = Estimate, label=""), position = position_nudge(y = -0.8), inherit.aes = F)

@@

Subset.DR.plot <-Subset.DR.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0, size = 1,fill="black", colour="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-0.25, 0.25))+
  annotate("text", x=-0.22, y=1.5, label= expression(lambda[DR])) + xlab(" ") + ylab(" ") + 
    geom_errorbarh(data = HPD_Interval_DR_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  theme(panel.grid.major.y = element_blank())

@@

Subset.B.plot <-Subset.B.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="orange", colour="black")+
  geom_jitter(shape = 21, alpha = 0, size = 1,fill="black", colour="orange")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-0.25, 0.25)) +
  annotate("text", x=-0.20, y=1.5, label= expression(lambda[BAMM])) +
  geom_errorbarh(data = HPD_Interval_B_PC, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "orange", size = 1) +
  xlab("Estimate (paternal care)") + ylab("") +
  theme(panel.grid.major.y = element_blank())

@@

Subset.ND.plot2 <-Subset.ND.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6), fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0, size = 1, colour="black", fill="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-2.5, 4)) +
  xlab(" ") + ylab(" ") +
    geom_errorbarh(data = HPD_Interval_ND_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

@@

Subset.DR.plot2 <-Subset.DR.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0, size = 1,fill="black", colour="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")+ scale_x_continuous(limits = c(-2.5, 4)) +
  xlab(" ") + ylab(" ") +
  geom_errorbarh(data = HPD_Interval_DR_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

@@

Subset.B.plot2 <-Subset.B.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6),fill="darkturquoise", colour="black")+
  geom_jitter(shape = 21, alpha = 0, size = 1,fill="black", colour="darkturquoise")+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none") + scale_x_continuous(limits = c(-2.5, 4)) +
  xlab("Estimate (sexual size dimorphism)") + ylab("") +
  geom_errorbarh(data = HPD_Interval_B_W, aes(y = Parameter, xmin = lower, xmax = upper), 
                 inherit.aes = F, height = 0, position = position_nudge(y = -0.5), colour = "darkturquoise", size = 1) +
  theme(panel.grid.major.y = element_blank())

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.DR.pgls.summary <- dr.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|Intercept")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% polygyny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% polygyny", 
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.DR.pgls.summary$Parameter <- factor(Subset.DR.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% polygyny", "5-20% polygyny", ">20% polygyny"))

@@

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.ND.pgls.summary <- nd.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|Intercept")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% polygyny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% polygyny",
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.ND.pgls.summary$Parameter <- factor(Subset.ND.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% polygyny", "5-20% polygyny", ">20% polygyny"))

@@

# Subrtact the intercept (monogamy) from the partial estimates to get their estimated effect on speciation rate in comparison to the reference level (monogamy)
Subset.B.pgls.summary <- b.mating %>% 
  dplyr::bind_rows() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI")) %>% #estimate now in 5th col
   dplyr::filter(str_detect(string = Parameter, "mating_system|(Intercept)")) %>% 
  dplyr::mutate(Parameter = case_when(Parameter == "as.factor(mating_system)1" ~ "<5% polygyny",
                                      Parameter == "as.factor(mating_system)2" ~ "5-20% polygyny", 
                                      Parameter == "as.factor(mating_system)3" ~ ">20% polygyny", 
                                      TRUE ~ Parameter))

#Factor for plot display
Subset.B.pgls.summary$Parameter <- factor(Subset.B.pgls.summary$Parameter, 
                                           levels = c("(Intercept)", "<5% polygyny", "5-20% polygyny", ">20% polygyny"))
